\noindent
{\bf Leadership \& Outreach} \\
\vspace{-9mm}
\begin{center}
\rule{\textwidth}{0.2mm}
\end{center}
\vspace{-3mm}


\noindent \textbf{\href{https://astronomyontap.org/event/astronomy-on-tap-baltimore-january-edition/}{Astronomy on Tap (AoT) Baltimore}, Guilford Hall Brewery, Baltimore, MD, Jan 2024} \\
- General Public Talk: ``Stellar Cheers: A Toast to the Eccentricities of RV Tauri Binary Stars.''
\vskip 0.2in

\noindent
{\textbf{\href{https://www.spaceappschallenge.org/2023/locations/hermosillo/?tab=schedule}{NASA International Space Apps Challenge -- Hermosillo}, Local Mentor and Judge, Tecnol\'{o}gico de Monterrey Campus Sonora Norte, Hermosillo, Sonora, M\'{e}xico, Oct. 6--8, 2023}

\noindent
- Engaged with student groups, offering advice as they worked on their projects. Evaluated student presentations at the conclusion of the hackathon. Presented a talk about my academic journey to the PhD, highlighting key experiences and insights. Delivered a scientific talk to professors and graduate students at the university.

\vskip 0.2in


\noindent
\textbf{Better Astronomy for the New Generation! (BANG!) Organizing Committee Member, Sept. 2022 - May 2023} \\
- The University of Maryland's Astronomy Department's BANG! Seminar features speakers and discussions on issues of equity and inclusion, career paths, and soft skills for astronomers.
\vskip 0.2in

\noindent
\textbf{Research Mentor, Oct. 2020 - Jan 2021} \\
- Mentoring a high school senior in Madison County, VA, developing a research project on classifying M-dwarf flares based on the Solar-flare classification system.
\vskip 0.2in

\noindent
\textbf{Colorado Springs Cool Science Festival - Zoom-a-Scientist, Oct. 2020} \\
- Virtual (Zoom) chat sessions with children in Fairbanks, AK (3rd grade) and in Colorado Springs, CO (1st grade) about astronomy and what it's like to be a scientist.
\vskip 0.2in

\noindent
\textbf{Smithsonian National Air \& Space Museum Volunteer Astronomer, Oct.~2017~-~Present}\\
- \href{https://airandspace.si.edu/events/astronomy-chat-gabriella-alvarez-and-laura-vega-0}{Astronomy Chats}
% Museum-goers can video-chat or chat with me in person and ask questions about my research and what it is like to be an astronomer. \\
\& Hispanic Heritage Month Outreach: Innovators in Air and Space Family Day, Wash. DC.\\
% \vskip 0.1in

\noindent
\textbf{Barrera Veterans Elementary School - Career Day, Von Ormy, TX, May 2019 } \\
- Chat with children at different grade levels about astronomy and what it's like to be a scientist.
\vskip 0.2in

\noindent
\textbf{Bancroft Elementary Saturday Academy - Astronomy Chat, Wash. DC, January 2019} \\
- Visited 2nd and 3rd grade Latinx bilingual students at Bancroft Elementary to talk about astronomy and science. Presentation facilitated by the Smithsonian Air \& Space Museum and sponsored by the Smithsonian Latino Center. \\
\vskip 0.01in

\noindent 
\textbf{Smithsonian Astrophysical Observatory - Rising Stars Camp, St. Katharine Drexel, Roxbury Crossing, MA, July 2018} \\
- Facilitated a number of activities such as the use of the Micro Observatory Robotic Telescopes and software to introduce the children to the life cycle of stars, and other astronomy topics. I also gave a short talk about my research.  \\
\vskip 0.01in

\noindent
\textbf{Fisk-Vanderbilt Bridge Program Recruitment at SACNAS, Long Beach, CA, Oct 2016} \\
- Booth at SACNAS to recruit undergraduate student for the Fisk-Vanderbilt Bridge Program. \\
% - Attended the National Society for Hispanic Physicists. \\

\vskip 0.01in
\noindent
\textbf{DCA Stars at The University of Maryland - College Park, Summer 2016} \\
- Students and mentors met weekly and discussed our research, goals, setbacks, and successes. \\

\vskip 0.01in
\noindent
\textbf{Inclusive Astronomy Conference at Vanderbilt, Nashville, TN, June 17--19, 2015} \\
- Volunteer host for the inaugural conference on diversity and inclusion. \\

\vskip 0.01in
\noindent
\textbf{Astronomy Torus 2012 Workshop at UTSA, San Antonio, TX, December 5--7, 2012} \\
- International workshop focused on active galactic nuclei; Local Organizing Committee Member: Logistics planning; Registration desk. \\

\vskip 0.01in
\noindent
\textbf{Toastmasters International, Oct. 2013--Present} \\
- Goddard Toastmasters Vice President of Public Relations (06/2022-Present); Vanderbilt Toastmasters Vice President of Public Relations (05/2015-Present); UTSA Roadrunner Toastmasters Treasurer (01/2014-07/2014); Deliver prepared and extemporaneous speeches as well as evaluating other speakers. \\

\vskip 0.01in
\noindent
\textbf{Society for Advancement of Chicanos \& Native Americans in Science (SACNAS)} \\
- Founding officer (Treasurer) for the {\it first} SACNAS chapter in the state of Tennessee. \\
% - Hosted an abstract workshop for the 2015 SACNAS Conference. Gave tips and advice on how to make a good scientific abstract. \\

\vskip 0.01in
\noindent
\textbf{The Physics Honor Society \text{\textbar} Sigma Pi Sigma at UTSA – President, Apr. 2013--Jan. 2014} \\
- Organized student study sessions for the Physics GRE; Tutored students in physics and Mathematics; Supplemental officer for Society of Physics Students: Public Relations \& Secretary. \\

\vskip 0.01in
\noindent
% \newpage
\textbf{Society of Physics Students at UTSA} \\
- \textbf{\textit{Outreach}}: Various on-campus STEM outreach events for high school students like Nano Day with Partnership for Education \& Research in Materials at UTSA \& Hispanic Chamber of Commerce’s CORE4 STEM Familia Day Expo at UTSA; Space Day for elementary school children at Forest Hills Public Library; Student Panelist for Engineering-Day at UTSA; On-campus liquid-nitrogen ice cream sales with physics demonstrations. \\
- \textbf{\textit{Public Relations Officer}}: Made posters and flyers of meetings, fundraisers, talks, and events; Managed social media accounts such as SPS’ Facebook page; UTSA Physics \& Astronomy`s “Friday Nights, Celestial Lights” monthly outreach event. \\
% \indent - Promoted the visit of Nobel Laureate John C. Mather and of Sir Roger Penrose to UTSA \\
% \end{list}